\bf Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-19 notes/notes.tex
obtained Add and Adz at Ub=-U/10

\subsection{Impurity spectral function \(A_{dd}(\omega)\)}
These are the frequency-domain spectral functions for the retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{d\sigma}\right\}  \right>\):
\begin{center}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.100.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.133.pdf}\\
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.182.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}\\
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.26.pdf}
\end{center}

\subsection{Impurity-bath off-diagonal spectral function \(A_{dz}(\omega)\)}
These are the frequency-domain spectral functions for the off-diagonal retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{0\sigma}\right\}  \right>\):
\begin{center}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.100.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.133.pdf}\\
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.182.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.250.pdf}\\
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.26.pdf}
\end{center}

>>>>

\clearpage
\subsection{Impurity spectral function \(A_{dd}(\omega)\)}
These are the frequency-domain spectral functions for the retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{d\sigma}\right\}  \right>\):
\begin{center}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.145.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.188.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
\end{center}

\subsection{Impurity-bath off-diagonal spectral function \(A_{dz}(\omega)\)}
These are the frequency-domain spectral functions for the off-diagonal retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{0\sigma}\right\}  \right>\):
\begin{center}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.100.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.145.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.188.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.250.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.26.pdf}
\end{center}
